Quantum Hoare Type Theory

### 2020-06-12 ms-paper/ms-paper.tex
Almost done proof for typechecking HQW

\begin{mathpar}
	\inferrule
	{ \exists \Psi . (emp * \top) \vdash q \Leftarrow mkQbit false; return measQbit q \chk r : Bool . \forall \Psi . (emp \multimap emp \wedge Id(r, false)) }
	{do (q \Leftarrow mkQbit false; return measQbit q) \chk \{emp\} r : Bool \{emp \wedge Id(r, false)\}}
\end{mathpar}

>>>>

WIP derivation tree for above program:

\begin{mathpar}
	\inferrule*[right=HIntro]
	{\inferrule*[right=consq]
		{\inferrule*[right=mkQbit]
			{\inferrule*[right=measQbit]
				{\inferrule*[right=return]
					{q : \type{Qbit}, r : \type{Bool} \vdash r \chk \type{Bool}}
					{q : \type{Qbit}, r : \type{Bool}; P_1 \circ ((q \mapsto -) \multimap emp) \vdash \kw{return} r \syn r : \type{Bool} . R}
					\\ q : \type{Qbit} \vdash q \chk \type{Qbit}
					\\ \cdot; P_0 * (q \mapsto \ket{0}) \prove (q \hookrightarrow -)
				}
				{q : \type{Qbit}; P_0 * (q \mapsto \ket{0}) \vdash r \Leftarrow \kw{measQbit} q; E_3 \syn r : \type{Bool} . (\exists r : \type{Bool}.R)}
				\\ \cdot \vdash \kw{false} \chk \type{Bool}
			}
			{
				\cdot; P_0 \vdash q \Leftarrow \kw{mkQbit false}; E_{23} \syn r : \type{Bool} . (\exists q : \type{Qbit}.R)
			}
			\\ r : \type{Bool}; i,m ; R \prove emp \multimap emp \wedge Id(r, \kw{false})
		}
		{
			\cdot; \lambda i . \lambda m . i = m \wedge (emp * \lambda m' \top)m \vdash E_1; E_{23} \chk r : \type{Bool} . (emp \multimap emp \wedge Id(r, \kw{false}))
		}
	}
	{\cdot \vdash \kw{do} E \chk \{emp\} r : \type{Bool} \{emp \wedge \kw{Id}(r, \kw{false})\}}
\end{mathpar}
